Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-11-06 appendix.tex
app

\section{Supplementary Information}

@@

(1) Security: Adversarial attacks may raise security considerations on deep
learning applications, and even cause negative effect.
%
In contrast, in this manuscript, we focus on defending against the attacks and
enhancing a model's adversarial robustness, and hence is expected to have a
positive impact instead.

(2) Environment: Although adversarial training is not environment-friendly due
to its high training cost (in terms of more intensive computation than regular
training), our method has significantly improved the adversarial training
efficiency compared to the previous works (hence is a little bit more
environment-friendly).

\textbf{Limitations.}
%
\begin{quote}

Considering the limitations of an approach is an important part of good
academic scholarship. While many high-quality CVPR papers thoroughly consider
and discuss limitations, CVPR 2022 aims to emphasize the importance of an
honest treatment of limitations. Authors are thus explicitly encouraged to
discuss limitations, ideally by creating a separate "Limitations" (sub-)section
in their papers.

Such discussion shall point out any strong assumptions and how robust the
results are to violations of these assumptions (e.g., independence assumptions,
noiseless settings, model well-specification, asymptotic approximations only
held locally). Authors need to reflect on how these assumptions might be
violated in practice and what the implications would be.

The discussion shall also reflect on the scope of their claims, e.g., if the
authors only tested their approach on a few datasets or did a few runs. In
general, empirical results often depend on implicit assumptions, which should
be articulated. The discussion shall reflect on the factors that influence the
performance of the approach. For example, a recognition algorithm may perform
poorly when image resolution is low or images are taken in low lighting.

We understand that authors might fear that complete honesty about limitations
might be used by reviewers as grounds for rejection. It is worth keeping in
mind that a worse outcome might be if reviewers discover limitations that are
not acknowledged in the paper. In general, we advise authors to use their best
judgement and recognize that individual actions in favor of transparency play
an important role in developing norms that preserve the integrity of the
community. Reviewers will be specifically instructed to not penalize honesty
concerning limitations

\end{quote}

>>>>

\section{Additional Information}

@@

(1) \ul{Security:} Adversarial attacks may raise security considerations on
deep learning applications, and even cause negative effect.
%
In contrast, in this manuscript, we focus on defending against the attacks and
enhancing a model's adversarial robustness, and hence is expected to have a
positive impact instead.

(2) \ul{Environment:} Although adversarial training is not
environment-friendly due to its high training cost (in terms of more intensive
computation than regular training), our method has significantly improved the
adversarial training efficiency compared to the previous works (hence is a
little bit more environment-friendly).

\noindent\textbf{II. Limitations.}

(1) \ul{The assumption that an ``intermediate point'' exists between regular
training of DML model and min-max adversarial training of DML model.}
(discussed in \cref{sec:1}; this is the motivation of HM)

We propose the flexible tool HM where regular training and min-max adversarial
training are equivalent to its boundary cases.
%
By adjusting the destination hardness $H_\mathsf{D}$ in HM, we can obtain
different results from adversarial training.
%
In the experiments section, we empirically search for valid options of the
destination hardness, and add further improvements (\ie, LGA and ICS) on top of
them.
%
The proposed method has been validated on three commonly used dataset, which
demonstrates its robustness empirically.

Even if the proposed method stopped working in a new dataset or with some other
different experimental settings, we can reduce
the value $H_\mathsf{D}$ towards $H_\mathsf{S}$ until this method works.
%
Since HM falls back into regular training when $H_\mathsf{D}=H_\mathsf{S}$,
we believe our proposed method will work before $H_\mathsf{D}$ is reduced
to $H_\mathsf{S}$.

Hence, this assumption is not expected to be a limitation.

(2) \ul{The assumption on optimization of the HM objective.}
(discussed in \cref{sec:31})

Our proposed method HM does not rely on an optimizer that can really optimize
the HM objective to zero.
%
In contrast, the state-of-the-art defense ACT~\cite{robrank} relies on the
optimizer to successfully push the adversarial positive sample and adversarial
negative sample close to each other in the embedding space.
%
This is hard to achieve given a low adversarial training budget (\eg, $\eta=8$),
as can be shown in our experiments and acknowledged by \cite{robrank}.

(3) \ul{The assumption that $H_\mathsf{D}$ should remain Semihard.}
(discussed in \cref{sec:32})

This is empirically supported by our experimental observations.
%
Even if this assumption is broken under some new experiment settings,
we can further reduce the range of $H_\mathsf{D}$ until our method works again,
thanks to the flexibility of HM.

(4) \ul{A factor that influence the performance of our approach, namely
backbone model.}

The backbone model significantly influences the performance in every aspect, as
the standard DML adopts ImageNet-initialized backbones for further training.
%
In this paper, we adopt ResNet-18 following the state-of-the-art
defense~\cite{robrank} for fair comparison.
%
Since our proposed defense method is independent to backbone selection, it is
expected to be effective on other backbone models as well.

(5) \ul{A factor that influence the performance of our approach, namely
adversarial training budget $\eta$.}

As demonstrated in our experiments, the adversarial training budget, namely the
maximum number of PGD iterations $\eta$ for creating the adversarial examples
can greatly influence the performance.
%
We conduct experiments with multiple choices of $\eta$, and we can see from the
curves that the model performance has a converging trend with large $\eta$
settings.

\noindent\textbf{III. Use of Existing Assets.}

(1) \ul{Datasets:} All the datasets used in our paper are public datasets,
and their corresponding papers are properly cited.

(2) \ul{Code and Implementation:} Our implementation is built upon PyTorch
and the public code of the state-of-the-art defense method~\cite{robrank}
(License: Apache-2.0).
